Dish: Distribution-oblivious Shell Scripting

### 2019-11-22 pldi/draft.tex
Updates

% https://ecommons.cornell.edu/bitstream/handle/1813/6508/85-668.pdf?sequence=1
% The growth of the web led to specialized frameworks for massively distributed computation~\cite{mapreduce:08, spark:10, naiad:13}.
% While they Moreover, these systems take advantage of functional purity;
%   for programs that are not data-intensive processing pipelines (\eg web servers), purely functional code is generally responsible for only a small fraction of the program runtime.
A plethora of systems assist in the construction of distributed software.
Distributed operating systems~\cite{rashid1981accent, walker1983locus, ousterhout1988sprite, mullender1990amoeba, pike1990plan9, rozier1991overview, dorward1997inferno, barak1998mosix, schwarzkopf2013dios, sacha2013osprey} and programming languages~\cite{erlang:96, acute:05, mace:07, cloudhaskell:11}
% simplify many of the problems of distribution and
provide a significant amount of automation. % but require development in a new system or language.  While they take care of all the distribution minutiae, 
However, they involve significant manual effort using the provided abstractions, which are strongly coupled with the underlying operating or runtime system.
\TODO{This has to be broken down into systems and PLs, coz systems are the most relevant/important class.}

\heading{Annotation-based Distribution}
Ignis and Mozart

@@

\heading{Concurrent and Distributed Shells}
Among other work, the Smoosh authors have argued that certain features of the shell are useful for concurrency~\cite{smoosh:18}.
However, their work is 
dgsh~\cite{dagsh:17}.

>>>>

% https://ecommons.cornell.edu/bitstream/handle/1813/6508/85-668.pdf?sequence=1
% The growth of the web led to specialized frameworks for massively distributed computation~\cite{mapreduce:08, spark:10, naiad:13}.
% While they Moreover, these systems take advantage of functional purity;
%   for programs that are not data-intensive processing pipelines (\eg web servers), purely functional code is generally responsible for only a small fraction of the program runtime.
A plethora of systems assist in the construction of distributed software.
Distributed operating systems~\cite{rashid1981accent, walker1983locus, ousterhout1988sprite, mullender1990amoeba, pike1990plan9, rozier1991overview, dorward1997inferno, barak1998mosix, schwarzkopf2013dios, sacha2013osprey} and programming languages~\cite{erlang:96, acute:05, mace:07, cloudhaskell:11}
% simplify many of the problems of distribution and
provide a significant amount of automation. % but require development in a new system or language.  While they take care of all the distribution minutiae, 
However, they involve significant manual effort using the provided abstractions, which are strongly coupled with the underlying operating or runtime system.
% TODO: \TODO{This has to be broken down into systems and PLs, coz systems are the most relevant/important class.}

\heading{Annotation-based Distribution}
Recent systems for light-touch distribution, Ignis~\cite{ignis:19} and Mozart~\cite{mozart:19}, give developers the ability to express through annotations;

Both work on high-level, managed languages---server-side JavaScript for Ignis and Python for Mozart---that allow runtime transformations without affecting the broader environment under which a program executes.
This is different

Annotations are used by ---complicated by the use of third-party libraries similar to \sys's extensions.
\sys is designed to be used, so it is somewhat more heavy-weight than Ignis' declarative recipes or Mozart's split annotations, but geared toward the deveopers of these components---not the users composing them.
As such..
Their annotations language is not as principled as \sys's---and one that is critical in ensuring that the dataflow analyses preserves the semantics expected by the developer
The side-effects present in the shell dwarf those of functional languages
The shell is also more general.

@@

\heading{Concurrent and Distributed Shells}
\nv{NV}
Among other work, the Smoosh authors have argued that certain features of the shell are useful for concurrency~\cite{smoosh:18};
Their work does not automatically parallelize pipelines, but rather argues that the shell language is itself an good DSL for concurrency;
This argument is different from \sys, 
an argument complementary to \sys's which automatically (and correcctly) parallelizes pipelines even when developers have---hence distribution-\emph{oblivious} shell scripting.

Several shells add support for non-linear pipe topologies;
  this 
2dsh~\cite{}
rc~\cite{}
gsh~\cite{}
dgsh~\cite{dagsh:17}.

Commands for explicitly specifying parallelism such \ttt{qsub}~\cite{gentzsch2001sun}, \textsc{SLURM}~\cite{yoo2003slurm}, calls to \textsc{GNU} \ttt{parallel}~\cite{Tange2011a}, or any manual rewriting~\cite{mapreduce:08, ciel:11, spark:12}.
These commands require the user to express the program explicitely, work only with embarrasingly parallel (and short) programs;
  \sys and scales out to large pipelines
Often, these commands provide options to support very special cases\footnote{
---a stark contradiction to the celebrated \unix philosophy.
For example, \tti{parallel}, an official GNU project, flags such as \ttt{--skip-first-line}, \ttt{-trim}, and \ttt{--xargs}, that a \unix user would achieve with \ttt{head}, \ttt{sed}, and \ttt{xargs}; it also includes other programs that 
with complex semantics, such as the ability transfer files between computers, separate text files, and parse CSV.

\heading{Dataflow Graph Model}

\nv{needs KM}
On our dataflow graph model: Our data flow graph model is
  different than most distributed batch and stream processing systems,
  since the shell is a hybrid between the two. Batch processing
  systems have no notion of data order, and stream processing systems
  usually have order, but none of these systems supports this notion
  of reading from different sources in sequence. Our dataflow graph
  model supports this by including information about incoming edge
  order. Another benefit of our dataflow model, is that together with
  the equations that hold on stateless and pure commands, data
  parallelism is exposed in the graph as task parallelism. This allows
  the unoptimized and optimized dataflow graph to have the same
  unified representation, and doesn't lead to an ad-hoc optimization
  of the dataflow graph as done in the other systems (the last bit is
  too aggressive).
